---
title: "Project 01"
author: "Zackery Jones"
date: "2026-03-02"
output:
  ioslides_presentation:
    incremental: false
  beamer_presentation:
    theme: Madrid
    colortheme: seahorse
    fonttheme: structurebold
    latex_engine: xelatex
    toc: false
    incremental: false
fontsize: 10pt
mainfont: Arial
header-includes:
- \usepackage{xcolor}
- \definecolor{accent}{HTML}{004C99}
- \setbeamercolor{structure}{fg=accent}
- \setbeamertemplate{footline}[frame number]
- \setbeamertemplate{section page}[none]
- \AtBeginSection{}
- \setlength{\parskip}{6pt}
- \setlength{\parindent}{0pt}
- \usepackage{listings}
- \lstset{basicstyle=\ttfamily\scriptsize, breaklines=true, columns=fullflexible,
  frame=single, backgroundcolor=\color{gray!5}}
- \setkeys{Gin}{width=0.75\linewidth,keepaspectratio}
- \AtBeginEnvironment{verbatim}{\scriptsize}
- \AtBeginEnvironment{alltt}{\scriptsize}
- \setbeamerfont{itemize/enumerate body}{size=\scriptsize}
- \setbeamerfont{itemize/enumerate subbody}{size=\scriptsize}
editor_options:
  markdown:
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
## Table of Contents

1) Setup
2) Data Understanding
3) Cleaning
4) Feature Engineering
5) Exploratory Data Analysis
6) Train/Test Split
7) Modeling
8) Threshold Choice
9) Evaluation
10) Interpretation
11) Discussion
12) Conclusion

## 1) Setup
Loading Dataset and Standardizing Column Names
```{r, eval=FALSE}
set.seed(1)
install.packages('janitor')
install.packages('skimr')
library(janitor) 
library(skimr)
df <- read_csv('UCI_Credit_Card.csv')
cleaned <- clean_names(df)
skim(df)
summary(df)
```

## 2) Data Understanding

Target is default_payment_next_month
these mean w/e

## 3) Cleaning

No missing values
lots of categorical
non predictive idk

## 4) Feature Engineering

xx
```{r, message=FALSE, warning=FALSE, echo=TRUE}
install.packages('readr')
library(readr)
df <- read_csv("UCI_Credit_Card.csv")
```
summary
graphs

## 6) Train/Test Split

rsample package

## 7) Modeling

baseline
tree based

## 8) Threshold Choice

## 9) Evaluation

confusion matrices
ROC/AUC

## 10) Interpretation

What appears influential
## 11) Discussion
potential concerns
limitations


## 12) Conclusion
which model we reccomend
realistic next steps for improvement


## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r, echo = TRUE}
df <- read.csv('UCI_Credit_Card.csv')
summary(df)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

